Network Configuration Synthesis with Abstract Topologies

### 2016-11-14 paper/abstraction/paper.tex
tweaks

One observation is that the spine template configuration and concrete spine configurations are structured similarly. We formalize this idea by defining a simple, vendor-neutral language for BGP configurations called \mbgp and formally define compilation for policies over both concrete and abstract topologies to \mbgp. In addition we define a two concretization ($con$) functions that translates an abstract \sysname policy and \mbgp configuration to a concrete \sysname policy and concrete \mbgp configuration respectively. Concretization takes a context $\Gamma : \mathit{Var} \rightarrow 2^{\mathit{Prefix} \times V}$ that maps each template variable to a set of pairs of a concrete prefix and topology location where the prefix is owned. Intuitively, the spine template in concretized by replacing each abstract role with the set of all concrete routers that map to that role and each prefix template variable with a new entry in the configuration for each individual prefix provided by the context $\Gamma$.
The main theoretical result is that the compilation and concretization functions commute:

@@

However, template variables tell us exactly where this kind of change can happen. The only way in which the spine routers depend on anything non-local is in the match on prefix template variables. Instead, we can associate a new unique community tag for template variable {\small \$GP} and then replace each match on {\small \$GP} with a test on the new community tag. The new ToR must now simply attach the new community tag to advertisements for its prefixes so downstream routers can just match the community tag. Figure~\ref{fig:bgp-configs} (right) shows the templates after the transformation.

>>>>

One observation is that the spine template configuration and concrete spine configurations are structured similarly. We formalize this idea by defining a simple, vendor-neutral language for BGP configurations called \mbgp and formally define compilation for policies over both concrete and abstract topologies to \mbgp. In addition we define two concretization ($con$) functions that translate an abstract \sysname policy and \mbgp configuration to a concrete \sysname policy and concrete \mbgp configuration respectively. Concretization takes a context $\Gamma : \mathit{Var} \rightarrow 2^{\mathit{Prefix} \times V}$ that maps each template variable to a set of pairs of a concrete prefix and topology location where the prefix is owned. Intuitively, the spine template is concretized by replacing each abstract role with the set of all concrete routers that map to that role and each prefix template variable with a new entry in the configuration for each individual prefix provided by the context $\Gamma$.
The main theoretical result is that the compilation and concretization functions commute:

@@

However, template variables tell us exactly where this kind of change can happen. The only way in which the spine routers depend on anything non-local is in the match on prefix template variables. Therefore, we can avoid having to modify the configurations for the spine routers by associating a new unique community tag for template variable {\small \$GP} and then replacing each match on {\small \$GP} with a test on the new community tag. The new ToR must now simply attach the new community tag to advertisements for its prefixes so downstream routers can match against it. Figure~\ref{fig:bgp-configs} (right) shows the templates after the transformation.
